Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
more results

\begin{figure}[t]
\centering
\plotone{initial_model_paper}
\caption{\label{fig:initial_models} Our ``cool'' (solid) and ``hot''
  (dashed) initial models, showing both the density and temperature.}
\end{figure}

@@

@@

\begin{figure}[t]
\centering
\plotone{plots/results/baroclinicity}
\caption{\label{fig:baroclinicity} Baroclinicity. This plot shows
$\ln \left(\mathbf{\psi}\right)$ at time $t = 0.02~\mathrm{s}$.}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\epsscale{0.75}
\plotone{initial_model_paper}
\caption{\label{fig:initial_models} Our ``cool'' (solid) and ``hot''
  (dashed) initial models, showing both the density and temperature.}
\epsscale{1.0}
\end{figure}

@@

A final feature worth noting is the ash that seems to move along the
surface at a higher velocity than the flame, via surface gravity
waves.  The sponging that we perform is likely damping this some, and
the method by which we initialize the flame may induce a larger
transient than in nature, nevertheless, this surface ash is intriguing
because it affects the composition of the photosphere ahead of the
burning front, potentially changing our interpretation of
observations.  This is something that will be explored more fully in
the future.

@@

\begin{figure}[t]
\centering
\plotone{plots/results/baroclinicity}
\caption{\label{fig:baroclinicity} Baroclinicity. This plot shows
$\ln \left(\mathbf{\psi}\right)$ at time $t = 0.02~\mathrm{s}$ for the 10/10 simulation.}
\end{figure}
